---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

# vir 

## Overview

This package includes a set of variational and stochastic variational algorithms
to estimate parameters in linear and probit regression with shirkage priors. The
algorithms are implemented using RcppEigen and don't require linking with any
other external libraries.

## Installation

Install the package using `devtools`
```{r, eval = FALSE, message = FALSE}
devtools::install_github("suchitm/vir")
```

## Usage
The functions in the package are named according to the link function, `lm` for
normal linear models and `probit` for binary regression, followed by the
shrinkage prior type: `ridge`, `lasso`, `hs`, `uninf`; and then the algorithm:
`gibbs`, `cavi`, or `svi`. Therefore, if an analyst wishes to use the svi
algorithm with a linear model and horseshoe prior, they can call the function
`lm_hs_svi` to analyze the data.
```{r}
library(vir)
set.seed(42)
X = matrix(nrow = 100, ncol = 5, rnorm(5 * 100))
colnames(X) = paste0('X', 1:5)
b = rnorm(5)
y = rnorm(1) + X %*% b + rnorm(100)
ridge_cavi_fit = lm_ridge_cavi(y, X, verbose = F, n_iter = 100, rel_tol = 0.0001)
```
The function outputs a nested list containing the names of the parameters and their optimal variational distributions. 
```{r}
names(ridge_cavi_fit)
names(ridge_cavi_fit$b)
ridge_cavi_fit$b$dist
ridge_cavi_fit$b$mu
```
The parameters can be summarised by: 
```{r}
summary_vi(ridge_cavi_fit, level = 0.95, coef_names = colnames(X))
```

### Prediction
Using the model fit, predictions can be generated using the predict functions named after the link and the algorithm (`vi` or `gibbs`)
```{r}
X_test = matrix(nrow = 5, ncol = 5, rnorm(25))
predict_lm_vi(ridge_cavi_fit, X_test)
```
